---
title: "Create a Scatter Plot from a Dataframe"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Package Description

This package provides a function that creates a scatter plot from two specified numeric columns in a dataframe. Users can customize the plot by adjusting axis labels, colors, and additional `geom_point()` parameters. This is particularly useful for quick and professional visualizations of the relationship between two numerical variables.

## Installation

You can install version 0.1.3 of the package from Github using the following command in your R Studio Console. Make sure that the `devtools` package is installed prior to this.

``` r
devtools::install_github("AlisonLuo/plotter", ref = "0.1.3")
```

## Example

Below are some examples of how to use the `scatter()` function in the `plotter` package. Keep in mind that two of the three examples use the `penguins` dataframe, so make sure to load the palmerpenguins package using `library(palmerpenguins)`.

```{r}
# load necessary packages
library(plotter)
library(palmerpenguins)
```

Example 1 using the penguins dataset
```{r example1}
scatter(penguins, bill_length_mm, bill_depth_mm)
```

Example 2 using a different dataset (mtcars) and incorporating custom axis labels
```{r example2}
scatter(mtcars, hp, mpg, 
        x_label = "Horsepower", 
        y_label = "Miles Per Gallon")
```

Example 3 using the penguins dataset, colouring points by species and customizing point size
```{r example3}
scatter(penguins, bill_length_mm, bill_depth_mm, 
        x_label = "Bill Length (mm)", 
        y_label = "Bill Depth (mm)", 
        colour = "species",     # Colour points by species
        size = 3,               # Customize point size
        alpha = 0.5)            # Adjust transparency of points
```

## License
This package is licensed under the MIT License.
